---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# readAOFM

{readAOFM} exists with the goal of making it easier to download data from the AOFM's datahub.

The package enables you to read most of the datasets from the [AOFM's datahub](https://www.aofm.gov.au/data-hub) with the exception of *Other Historical Datasets.*


## Installation

<!-- You can install readAOFM from [GitHub](https://github.com/) with: -->

<!-- ``` r -->
<!-- # install.packages("devtools") -->
<!-- devtools::install_github("joel23978/readAOFM") -->
<!-- ``` -->

## Example
```{r example, eval = F}
library(here)
source(here("script", "tidy_data.R"))

print(read_aofm("tb", "issuance"))

```


```{r example2, echo=FALSE, warning=FALSE, message=FALSE}
library(here)
source(here("script", "tidy_data.R"))

print(read_aofm("tb", "issuance"))

```

The read_aofm function takes up to four arguments:

- security, ## options include; tb, tib, tn, slf, summary, aggregate, ownership, retail, term.premium
- type, ## options include; dealt, settlement, issuance, syndication, buyback, turnover
- csv = FALSE, ## defaults to FALSE, if TRUE it will output a csv to /ouput with the cleaned data
- data.index = index, ## an index of data on the AOFM website, pulled from index.R

The function needs to be written to an object like the below:

- Where the excel files has multiple sheets the data is written to a list object with a list element for each sheet.
- The "Notes" sheet in the orignal files is not read into R

```{r example3, eval = F}
tb_issuance <- read_aofm("tb", "issuance")

```



To see the index of files/arguments to pass, use:
```{r}
browse_tables()
```


download.R contains two functions:

- download_aofm_xlsx() enables you down a single file (or all data files) from the AOFM's website to a /data subfolder
  - if no argument is passed; it will download all files from the AOFM's webite
  - if an argument with multiple matches is passed it will download all matching tables
  - if two arguments are passed (security, type) it will download the specific table
- find_file() takes arguments for (security, type) and returns a table id




## Disclaimer

The AOFM website may, at any time, change in such a way that the package stops working (esp if they change the structure of the files).

This package is not affiliated with or endorsed by AOFM, all data is provided under any terms set out on the AOFM website.


